---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# seastackplot

The goal of seastackplot is to create graphs that accurately represent the distribution and summary statistics of data.

## Installation

You can install the development version of seastackplot from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("Al-Stu/seastackplot")
```

## Creating a sea stack plot

The easiest way to plot a sea stack plot is using the `sea_stack_plot()` function. As an example, we will create a graph of how price differs between different diamond cuts using the 'diamonds' data set from the `ggplot2` package. To create a sea stack plot using the `sea_stack_plot()`, you need to make sure your data is long format (see here for an explanation of long vs wide format data http://www.cookbook-r.com/Manipulating_data/Converting_data_between_wide_and_long_format/). 

To plot a default sea stack plot with mean and standard deviation, the `sea_stack_plot()` function required the following variables:
* `data` your long format data frame or tibble
* `data.column` the name of the column your values are in
* `group.column` the name of the column your group names are in

```{r example}
library(seastackplot)

sea_stack_plot(data = ggplot2::diamonds,
               data.column = 'price',
               group.column = 'cut',
               bin.width = 1000, # bin.width defaults to 1, for this data that is
                                # too high resolution so we set it to 1000
               show.confidence.int = T
               )
```

The `sea_stack_plot()` function also includes the following variables for plot customisation:
* `data.label` the desired title for the data axis, if left NULL (default), will be the value of data.column

* `bin.width` the bin width being used to plot

* `mean.size` the size of the diamond showing the mean, measured in mm

* `median.size` the size of the point showing the median, measured in mm

* `orientation` "vertical" or "horizontal", whether or not the plot is being plotted vertically (default) or horizontally

* `show.mean` whether the mean should be plotted

* `show.median` whether the median should be plotted

* `show.standard.dev` whether the standard deviation rectangle should be plotted

* `show.confidence.int`	whether the confidence interval should be plotted

* `show.quantiles` whether the confidence interval should be plotted

* `ci.line.length` the length of the 'ticks' showing the upper and lower bounds of the confidence interval, measured on the same scale as the histogram

* `ci.line.length` the length of the 'ticks' showing the upper and lower bounds of the confidence interval, measured on the same scale as the histogram

```{r plot showing all stats}
sea_stack_plot(data = ggplot2::diamonds,
               data.column = 'carat',
               data.label = 'Carat',
               group.column = 'cut',
               bin.width = 0.2,
               show.mean = F, 
               show.standard.dev = F, # as mean and standard deviation shows by default need to manually silence them
               show.median = T,
               # show.quantiles = T,
               # quant.line.length = 300,
               median.size = 3
               )
```
